\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
space point -> point in space
"There is problem"

In FLUKA every single space point needs to be associated with one and only one region. There is problem 
when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
need to have the daughter  solids $S_{{\rm daughter},i}$ subtracted. So a solid which can be converted 
to a region $S_{\rm region}$ is then 
\begin{equation}
S_{\rm region} =  S_{\rm logical} - S_{\rm daughter,1} - S_{\rm daughter,2} - S_{\rm daughter,3} \ldots 
\label{eqn:logicalSubtraction}
\end{equation} 
If a logical volume has  number of daughter volumes which are also possibly Boolean solids, then computing 
$S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and 
\ref{eqn:setIntersection}.

>>>>

In FLUKA every single point in space needs to be associated with one and only one region. This presents a problem 
when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
need to have the daughter  solids $S_{{\rm daughter},i}$ subtracted. So a solid which can be converted 
to a region $S_{\rm region}$ is then 
\begin{equation}
S_{\rm region} =  S_{\rm logical} - S_{\rm daughter,1} - S_{\rm daughter,2} - S_{\rm daughter,3} \ldots 
\label{eqn:logicalSubtraction}
\end{equation} 
If a logical volume has  number of daughter volumes which are also possibly Boolean solids, then computing 
$S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and 
\ref{eqn:setIntersection}.
